\documentclass[11pt]{letter}
\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage{fullpage}

\renewcommand{\closing}[1]{\par\nobreak\vspace{\parskip}%
  \stopbreaks
  \noindent
  \ifx\@empty\fromaddress\else
  \hspace*{\longindentation}\fi
  \parbox{\indentedwidth}{\raggedright
       \ignorespaces #1\\[2\medskipamount]%
       \ifx\@empty\fromsig
           \fromname
       \else \fromsig \fi\strut}%
   \par}

\longindentation=0pt

\signature{Klaus Okkelberg}
\address{Klaus Okkelberg \\ 8488 Cherry Oak Ct \\ Mobile, AL 36695 \\ (484) 226 8020 \\ klaus.okkelberg@gmail.com}

\begin{document}

\begin{letter}{}
\opening{Dear Sir/Madam:}

I would like to apply for an internship for summer 2016 in electrical engineering.
% begin customize
%
% end customize
I am currently a PhD student in Electrical Engineering at Georgia Tech. I have a B.S.\ from Penn State and a M.S.\ from the University of New Orleans, both in Electrical Engineering. I offer a strong academic background and have a lot of experience in many areas. Highlights include:

\begin{itemize}
    \item \textbf{Academic Excellence:} B.S.\ GPA: 3.8, M.S.\ GPA: 4.0; wrote theses for both degrees. Anticipated PhD GPA of 3.8.
    \item \textbf{Numerous Research Areas:} Signal integrity at Xilinx, Battery management at Georgia Tech and the University of New Orleans, and Nuclear magnetic specstroscopy at Penn State. Also completed projects in quantum mechanics, vehicle stabilization, image/video correction, visual object detection, machine learning, and mathematics
    \item \textbf{Teamwork:} Lead Senior Design Project and several other school projects. Contributed to two research groups. Worked with Power/Signal Integrity engineers at Xilinx. Fostered group work among undergraduates as a TA.
    \item \textbf{Programming Skills:} 10+ years of experience with Matlab and Simulink, speeding up code by a factor of 100 at Penn State and by a factor of 15 at Xilinx, while adding functionality. Can also program in C, Java, Python, Fortran, and Visual Basic
    \item \textbf{Other skills:} Experienced with lab equipment, such as oscilloscopes and network analyzers. Good at mathematical modeling of physical systems
\end{itemize}

%I am eager to leverage my abilities to make a significant contribution to your company. My hours are flexible, and I will be available for up to 14 weeks beginning in May.

I look forward to learning about the next steps in the selection process. Thank you for your time and consideration.

\closing{Sincerely,}

\end{letter}

\end{document}
